### 2021-02-22 paper.Rmd
more intro
author list info update

---
author:
  - name: Stuart Lee
    affiliation: Monash University
    # use this syntax to add text on several lines
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    email: stuart.a.lee@monash.edu
  - name: Ursula Laa 
    affiliation: 
    address: |
      | Department of  ,
      |  University
  - name: Dianne Cook
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    affiliation: Monash University
    email: dicook@monash.edu
title:
  formatted: "An Overview of Tours for Dynamic Visualisation of High-dimensional Data"
abstract: > 
  Abstract goes here.
keywords:
  formatted: ["tours", "data visualisation"]
output: 
  bookdown::pdf_document2:
    template: template/wires_template_rmd.tex
    keep_tex: true
    toc: false
    citation_package: natbib
bibliography: references.bib
biblio-style: apalike
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.show = 'hold',
  dpi = 300 #,
  # out.width = "\\textwidth",
  # fig.path = here::here('img/')
)
```

@@

- Original tours (Di)
- Dataviewer, XGobi, GGobi, cranvas (XLispStat, Orca, mmvz) (Di)
- Alternatives (Stuart)

>>>>

---
author:
  - name: Stuart Lee
    affiliation: Monash University
    # use this syntax to add text on several lines
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    email: stuart.a.lee@monash.edu
  - name: Ursula Laa 
    affiliation: 
    address: |
      | Department of  ,
      |  University
  - name: Natalia da Silva
    address: |
      | Instituto de Estadística (IESTA), 
      | Universidad de la República
    affiliation: Universidad de la República
    email: natalia@iesta.edu.uy
  - name: Dianne Cook
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    affiliation: Monash University
    email: dicook@monash.edu
title:
  formatted: "An Overview of Tours for Dynamic Visualisation of High-dimensional Data"
abstract: > 
  Abstract goes here.
keywords:
  formatted: ["tours", "data visualisation"]
output: 
  bookdown::pdf_document2:
    template: template/wires_template_rmd.tex
    keep_tex: true
    toc: false
    citation_package: natbib
bibliography: references.bib
biblio-style: apalike
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.show = 'hold',
  dpi = 300 #,
  # out.width = "\\textwidth",
  # fig.path = here::here('img/')
)
```

@@

<!-- Original tours (Di)
- Dataviewer, XGobi, GGobi, cranvas (XLispStat, Orca, mmvz) (Di)
-->
- Alternatives (Stuart)
